---
title: "Data Cleaning (Text Format)-Kailash Hambarde(School Of Compuational Sciences,SRTMUN"
output: html_notebook
---

```{r}
Harmed<- readLines("C:\\Users\\Panu\\Documents\\Earthquake.txt")
```

Additional Siblings of 'readLines' These are some of the readLines functions supported R.

1) Read.csv   :-  For Comma separted values with period as decimal sepaator.
2) read.csv2  :-  For semicolon separated values with comma as decimal separator.
3) read.delim :-  Tab Delimated Fiiles with period as decimal separted.
4) read.delim2:-  Tab Delimated Fiiles with period as decimal separted.
5) read.fwf   :-  Data with predetermind numbers of bytes per columns.

-----------------------------
Data Cleaning
Now lets try to create Data Frame.
```{r}
d <- as.data.frame(Harmed)
```

A newly created data frame should always  be inspected. Before Proceeding forward let see what is that.
```{r}
d
```

Data Cleaning: Data Inspection:-

Data Inspection:-
-It Involves Inspecting data due to understand its structure, number of attributes and oberservations for each attributes and the data types for each these attributes.

-After reviewing this properties of data you are able to judge whether the raw data is representing aptly by the object inspected (lists,vectors,matrices,and data frame).

-d is the data frame but how good a data frame it is.? the following function will tell
```{r}
class(d)
```

class function tells the data type of variable.

```{r}
length(d)
```
length function returns the length of the object(vector,lists)

```{r}
nrow(d)
```
              
nrow function return the number of rows.

```{r}
ncol(d)
```

ncol function return the number of columns.

```{r}
dim(d)
```

dim function returns the dimesion of the object i:e number of rows and number of cloumns.

```{r}
str(d)
```

str() gives the structure of the data frame and tells that d conatins 9 oberservtions(rows) and 1 varibles(column).

--------------------------------------------------------------------------------------------------------
-----------------------------------------------------------------------------------------------------

So, after inspecting your data frame, the following conclusion 

1)  Data Frame have comments.

2)  The Attribute are not defined in separate columns.

3)  The data types are compromised.

Lets cleaning the data first.

--------------------------------------------------------------------------------------------------------

The Raw data that we want to analyze is in the txt format.

You wish to tackle the following problems.

* Step 1:-   Select the lines containing Data 

* Step 2:-   Remove the comments lines

* Step 3:-   Split the lines into separated fields

* Step 1:-   Transform into a data frame

* Step 1:- Normalize and coerce to correct type

-----------------------------------------------------------------------------------------------------
---------------------------------------------------------------------------------------------------

Data Cleaning : Select the lines containing data.

* grepl() function:- it is one of the string manipulation function in R.

Syntax :- grepl("^%",txt)


```{r}
comments <- grepl("^%",Harmed)
```

 - Here, the first argument of grepl is a search pattern, where the caret(^) indicates a start-of-line
 
 - The result of grepl is a logical vector that indicates which element of text contain the pattern'        start-of-line' followed by a percent sign i:e (%)comments
 
 - grepl() returns TRUE if a string contains pattern, otherwise FALSE; is the parameter is a string         vector, returns a logical vector
 
 
```{r}
comments
```
 
 
 - To Remove the selected comments we simple remove the vectors containing the comments form the text.
 
 
```{r}
display <- Harmed[!comments]
comments
```
 
---
*  String Manipulation Functions:-

- grep():-  This Function searches for matches  to pattern within each element of a character vector.

- Syntax:-  grep("^,txt")

- Let us run these functions and obeserve the outputs.



```{r}
comments_grepl <- grepl("^%",Harmed)
comments
```

```{r}
display_grepl <- Harmed[!comments_grepl]
display_grepl
```
```{r}
comments_grep <- grep("^%",Harmed)
comments_grep
```

```{r}
display_grep <- Harmed[!comments_grep]
display_grep
```

- Problem 1:- Suppose if we want to remove the very first digit from the string.
- Example  :- We have the following data.


```{r}
display[1]
```

- One way can be :- Run for loop until the total length of the string and replace the occurrence of the digit the whitespace.

-Solution :- Another way is to use the sub() built-in function in R.

```{r}
p <- display[1]
p
```

- Syntax :- sub(pattern, replacement , x)

- This functions finds patterns within string in a similar mannar in grep(), but then substitutes the first instance of a match with specified string.


```{r}
R <- sub("[[:digit:]]","",p)
R
```

- Problem 2 :- What if you want to replace all the occurrance of digit from the string.

- Solution  :- Use gsub() built in function in R .

- Syntax    :-  gsub(pattern, replacement, x)

This function works in exactly the same manner as sub(),but replaces all matches to pattern rather than replacing only the first match.We refer to this as global replacement.


```{r}
R <- gsub("[[:digit:]]","",p)
R
```
Syntax        :- sub(pattern. Replcement,x)
Syntax        :- gsub(pattern. Replcement,x)


- Pattern     : A pattern to search for, which is assumed to be a regular expression. Use an additinal                   argument fixed = TRUE to look for a pattern without using regular expression.


- Replecement : A character string to replace to occurrence(or occurrences for gsub) of pattern.

- x           : A chaacter vector to search the pattern. Each elecment will be searched separately

- replace the first occurrence of pattern with sub or replace all occurrences with gsub.


- Problem 3   :-  If you wish to know the character position of occurrence of 4 in the following.

```{r}
display[4]
```

- Solution    :-  Use regexpr() function

- This function reports the character postion in the provided strings where the start of the match with    pattern occurs.

- The function also returns the length of the match

```{r}
reg <- regexpr("4", display[4])
reg
```

- Problem 4  :-  As you can see here that there are 2 occurrence of 4. How can all such occurrence can be                 known?

- Solution  :-  Use grexpr() function

- This is globalversion of regexpr(). This function reports all matches to pattern rather than only the    first match. A list is returned in this case because if more than one match in an element of the         provided charater vector is possible.


-	grepl()	  :-  this function searches for matches to pattern and returns a logical vector containing the                 match
-	grep()		:-	Similar to grep() but returns an integer vector containing the match
-	Sub()		  :-	Similar to grep(), but it substituted the first instance of a match with a specified                      string
-	gsub()		:-	Tab-ame as sub(), but replaces all matches to pattern
-	regexpr 	:-	Returns the character position in the given strings where the start of the match with                     pattern occurs. Also returns length of the macth
-----------------------

- Data Cleaning : Split the lines in separate fields....  



So far, we have resolved the folowing problems with the data.

- Problem 1 : Select the lines containing data
- Problme 2 : Remove the comment lines

and have following data with us:

```{r}
display
```

- Problem 3 : we need a function which accepts a character vector and splits it into a list of character vectors

-	Solution	: Strsplit() does that

- This function accepts a character vector and a split argument which tells strsplit how to split a string into substrings. The result is a list character vectors.


```{r}
splitData <- strsplit(display,split = ",")
splitData
```


- Problem 4 :-  Trasform Into a Data Frame.

- The lines after splitting now are ready to be converted into a data frame.

- So, first all the elements are copied into matrix which is then coerced a data frame




```{r}
Lines<- matrix(unlist(splitData), nrow=length(splitData),byrow = TRUE)
```


- the function 'unlist' concatenates all the vectors in a list inti one large character vector That vector is then used to fill a matrix of class character


- byrow +TRUE : as the data is stored with rows concatenated

- stringAsFactor=FALSE: No interpretation of value is done



```{r}
Lines
```



```{r}
colnames(Lines) <- c("Name","DateOfBirth","DeathOfYear")
```

